Forecasting the black Sigatoka development rate:\\ A comparison of machine learning techniques

### 2017-05-01 conclusions.tex
2017-01-13-prueba
1-5 4.52

\subsection{Future work}

>>>>

The main findings were: 1) The highest R2 was 60\% 2) The highest R2 were reached with linear models like support vector regression with linear kernel, 3) As little as three meteorological variables can be used because of the correlations detected among variables.

\subsection{Future work}
Currently this research is focused on the extension of these findings to other farms and the extension of the model to be applied in an early warning system, which does not require the regression task.

### 2017-05-01 results.tex
1-5 4.52

\begin{table}[h] 
\caption{Composition of the Pareto frontier - La Rita} 
\label{tabla3} 
\centering
\begin{tabular}{c|c|c|c|c|c} 
\hline
\bfseries Variable & \bfseries Observation range & \bfseries Weeks ahead & \bfseries Technique &\bfseries $R^2$ & \bfseries $RMSE$\\ 
\hline\hline 
  &   &  &  &   &  \\

Pair $\overline{T}_{a}$ $\overline{W}$ &	1 to 1  & 36 & 64.25\% & 714.51 \\
 &	2 to 1  & 6 & 62.97\% & 695.10 \\
\hline 
All  & 1 to 1  & 18 & 62.98\% & 701.95 \\
   & 2 to 1  & 12 & 61.76\% & 679.92 \\
    & 3 to 1  & 6 & 60.60\% & 676.42 \\
    & 5 to 1  &  2 & 60.37\% & 672.39 \\
\hline    
$\overline{T}_{a}$ & 1 to 1  & 12  & 63.60\% & 708.77 \\
       &	2 to 1  & 4 & 62.23\% & 689.55 \\
\hline
\end{tabular} 
\end{table}

Similarly, the Pareto frontier for the 28 Millas farm is composed by 75 elements. The \tablename $.$\ref{tabla4} shows the composition about variables and observation ranges.

\begin{table}[h] 
\caption{Composition of the Pareto frontier - 28 Millas - Phase one} 
\label{tabla4} 
\centering
\begin{tabular}{c|c|c|c|c} 
\hline
\bfseries Variable & \bfseries Observation range & \bfseries Quantity & \bfseries Max $R^2$ & \bfseries Min $RMSE$\\ 
\hline\hline 
Pair $\overline{T}_{a}$ $\overline{W}$ & 1 to 1 & 8 & 57.80\% & 438.09 \\
\hline 
All   &	9 to 1 & 2 & 50.93\% & 397.93 \\
  & 10 to 1	 & 2 & 50.97\% & 398.81 \\
  &	8 to 1 & 6 & 51.62\% & 398.93 \\
  &	7 to 1 & 2 & 52.25\% & 400.28 \\
  &	6 to 1 & 2 & 53.16\% & 404.14 \\
  &	4 to 1 & 2 & 54.32\% & 407.54 \\
\hline    
$\overline{T}_{a}$ & 1 to 1  & 8  & 59.09\% & 439.44 \\
\hline
Pair $\overline{T}_{a}$ $\overline{H}$ & 1 to 1	 & 8 & 57.51\% & 428.61 \\
 &	2 to 1 & 20 & 56.91\% & 414.37 \\
 &	3 to 1 & 3 & 54.41\% & 411.55 \\
 &	4 to 1 & 3 & 53.34\% & 406.65 \\
\hline
Pair $\overline{T}_{a}$ $P$ & 3 to 1 & 9 & 56.23\% & 422.76 \\
\hline
\end{tabular} 
\end{table}

Now, the \figref{figura5} compares the mean of the $RMSE$ for each algorithm in the experiment, pero para la predicción de 1, 2 ó 3 semanas adelante con respecto a la información de las variables climatológocas y del preaviso biológico. Además, to predict one week ahead obtiene un RMSE más bajo que  two weeks ahead, and this is better than three weeks ahead. 
%
\begin{figure}[H] 
 \centering
 \includegraphics[scale=.5]{Usado_Algorithms-RMSE}
 \caption{$RMSE$ for each algorithm} 
 \label{figura5} 
\end{figure}

\figref{figura6} presents, for one, two and three weeks ahead, the best $R^2$. Results are group by farm. In general, to predict one week ahead is better than two weeks ahead and so on. The number of weeks consider in the observation range in the pattern is not the main discriminant factor, but it is clear that we get better $R^2$ for one week ahead than two weeks ahead and so on.

\begin{figure}[H] 
 \centering
 \includegraphics[scale=.5]{2017-01-15-Periods-R2}
 \caption{Phase one - Best $R^2$ for each observation range} 
 \label{figura6} 
\end{figure}

\figref{figura7} shows the best $R^2$ for each variables combination. Results are group by farm. The better results are obtained with $\overline{T}_{a}$ and the combination of $\overline{T}_{a}$ with $\overline{W}$, in both farms of similarly. You can note that the use of all variables in the model or the inclusion of the four variables suggest for expert criteria do not improve significantly the results, then the use of more sensors do not assure a better result.

\begin{figure}[H] 
 \centering
 \includegraphics[scale=.5]{2017-01-15-Variables-R2}
 \caption{Phase one - Best $R^2$ for each variable combination} 
 \label{figura7} 
\end{figure}

We can conclude that the best configuration in both farms is to consider the climate and the evolution stage of the current week to predict the evolution stage of the next week.

>>>>

\begin{table}[h] 
\caption{Composition of the Pareto frontier - La Rita} 
\label{tabla3} 
\centering
\begin{tabular}{c|c|c|c|c|c} 
\hline
\bfseries Variable & \bfseries Observation range & \bfseries Weeks ahead & \bfseries Technique &\bfseries $R^2$ & \bfseries $RMSE$\\ 
\hline\hline 
$\overline{T}_{a}$ $\overline{W}$ &	1  & 1 & SVR with linear kernel & 693.39 & 59.4\% \\
										&	2  & 1 & SVR with linear kernel & 683.22 & 59.4\% \\
\hline 
$\overline{T}_{a}$  &  5 & 1 &  SVR with linear kernel & 679.25 & 59.2\% \\
\hline 
$\overline{T}_{a}$ $\overline{H}$ &	5  & 1 & Elastic net & 677.49 & 57.8\% \\
										&	5  & 1 & SVR with linear kernel & 677.37 & 59.1\% \\
\hline										
\end{tabular} 
\end{table}
%
Similarly, the Pareto frontier for the 28 Millas farm is composed by 15 elements. The \tablename $.$\ref{tabla4} shows the composition about variables and observation ranges.

\begin{table}[h] 
\caption{Composition of the Pareto frontier - 28 Millas} 
\label{tabla4} 
\centering
\begin{tabular}{c|c|c|c|c|c} 
\hline
\bfseries Variable & \bfseries Observation range & \bfseries Weeks ahead & \bfseries Technique &\bfseries $R^2$ & \bfseries $RMSE$\\ 
\hline\hline 
$\overline{T}_{a}$ $\overline{H}$ $\overline{W}$ $P$  &	9  & 1  & Elastic net & 398.65 & 48.5\% \\
													&	8  & 1 & Elastic net & 399.57 & 48.8\% \\
													&	7  & 1 & Elastic net & 399.65 & 49.1\% \\													
\hline 													
$\overline{T}_{a}$ $\overline{H}$ $\overline{W}$  &	9  & 1  & SVR with linear kernel & 399.86 & 49.3\% \\
												&	7  & 1  & SVR with linear kernel & 400.87 & 50.3\% \\
												&	6  & 1  & SVR with linear kernel & 403.40 & 50.7\% \\
												&	3  & 1  & SVR with gaussian kernel & 407.25 & 90.7\% \\													
\hline 													
$\overline{T}_{a}$ $\overline{H}$  &	4  & 1  & Elastic net & 400.65 & 49.6\% \\
									&	1  & 1  & SVR with linear kernel & 412.26 & 51.8\% \\
									&	2  & 1  & SVR with linear kernel & 409.18 & 51.2\% \\			
\hline 																												
$\overline{T}_{a}$ $\overline{H}$ $P$  & 2  & 1  & SVR with linear kernel & 410.71 & 51.2\% \\
\hline 																												
All  & 7  & 1  & SVR with linear kernel & 426.19 & 51.9\% \\
     & 5  & 1  & SVR with linear kernel & 428.66 & 52.3\% \\
     & 5 & 1  & Elastic net & 433.03 & 52.4\% \\
     &  5 & 1  & Linear regression & 450.48 & 53.0\% \\          
\hline	
\end{tabular} 
\end{table}
%
Now, the \figref{figura6} compares the mean of the $RMSE$ for each technique in the experiment. Se muestra el $RMSE$ para la predicción de 1, 2 ó 3 semanas adelante con respecto a la información de las variables climatológicas y del preaviso biológico observadas. Se aprecia que to predict one week ahead obtiene un $RMSE$ más bajo que two weeks ahead, and this is better than three weeks ahead, lo cual es lo esperado pues entre más semanas adelante se desee predecir, hay más incertidumbre.
%
\begin{figure}[H] 
 \centering
 \includegraphics[scale=.5]{Usado_Algorithms-RMSE}
 \caption{$RMSE$ for each algorithm} 
 \label{figura6} 
\end{figure}
%
\figref{figura7} shows the the mean $RMSE$ for each variables combination. The better results are obtained with $\overline{T}_{a}$, $\overline{W}$ and $P$.  Incluir más variables en el modelo no asegura mejorar la métrica, lo cual es importante pues este resultado sugiere que the use of more sensors do not assure a better result of prediction. 
%
\begin{figure}[H] 
 \centering
 \includegraphics[scale=.5]{Usado_Variables-RMSE}
 \caption{$RMSE$ for each variable combination} 
 \label{figura7} 
\end{figure}
%
